Generative Synthesis of Insurance Datasets

### 2020-02-22 manuscript/manuscript.Rmd
typo
fix footnote

We make one key modification to the CTGAN implemention to accommodate our domain
specific datasets. During sampling of categories, we use the true data frequency
rather than the log-frequency. We find that using log-frequency causes the 
synthesizer to unrealistically oversample rare categories.

@@

To encourage usage, we implement an R interface to the original Python implementation
in the form of an open source package, **ctgan**.[^2]] We envisage this package to appeal to a 
variety of personas in the field. As examples, companies who are looking to crowd-source
insights into their data gain an option for data disclosure, and researchers working
with confidential data can release reproducible workflows along with a sample dataset. 
Depending on the use case, one can decide whether to share a single
sample dataset, or release a trained synthesizer, containing the generator only,
for users to generate data on demand.
In the latter case, one can further choose whether to make available the generator's
parameters, or to expose the generator through a Web service, while keeping the
model parameters private.

>>>>

We make one key modification to the CTGAN implementation to accommodate our domain
specific datasets. During sampling of categories, we use the true data frequency
rather than the log-frequency. We find that using log-frequency causes the 
synthesizer to unrealistically oversample rare categories.

@@

To encourage usage, we implement an R interface to the original Python implementation
in the form of an open source package, **ctgan**.[^2] We envisage this package to appeal to a 
variety of personas in the field. As examples, companies who are looking to crowd-source
insights into their data gain an option for data disclosure, and researchers working
with confidential data can release reproducible workflows along with a sample dataset. 
Depending on the use case, one can decide whether to share a single
sample dataset, or release a trained synthesizer, containing the generator only,
for users to generate data on demand.
In the latter case, one can further choose whether to make available the generator's
parameters, or to expose the generator through a Web service, while keeping the
model parameters private.
